---
title: "A simulated example with confounding bias"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

Here, we provide an example of using XMAP for correcting confounding bias in cross-population GWAS data. We simulated GWAS data with confounding effects. For demonstration, we assume that we have estimated the inflation constants $c_1=1.636171$ and $c_2=1.791455$, and the polygenic parameters $\Omega$ using bi-variate LDSC (See next section for details in estimating these parameters in real GWAS data).

We first fit XMAP without correcting confounding bias by setting $c_1=c_2=1$:
```{r}
library(susieR)
library(XMAP)
data("example_data_confound")
c1 <- 1.636171
c2 <- 1.791455
fit_xmapI <- XMAP(simplify2array(list(R1,R2)), cbind(zs1,zs2),
                  n=c(15000,20000), K = 5,
                  Omega = OmegaHat,
                  Sig_E = c(1,1),
                  tol = 1e-6,
                  maxIter = 200, estimate_residual_variance = F, estimate_prior_variance = T,
                  estimate_background_variance = F)
# Get credible set based on R1
cs1 <- get_CS(fit_xmapI, Xcorr = R1, coverage = 0.95, min_abs_corr = 0.1)
# Get credible set based on R2
cs2 <- get_CS(fit_xmapI, Xcorr = R2, coverage = 0.95, min_abs_corr = 0.1)
# Get joint credible set
cs <- cs1$cs[intersect(names(cs1$cs), names(cs2$cs))]
pip <- get_pip(fit_xmapI$gamma)
plot_CS(pip, cs, Beta_true[,1], main = "XMAP (C=I)")
```

In the above figure, the red dot is the only causal SNP, level-95\% credible sets are colored circles. Without correcting for confounding bias, some null SNPs on the left region of the locus can have high PIP. These are false positives.

Now, we use the estimated LDSC intercepts to correct the confounding bias in XMAP:
```{r}
c1 <- 1.636171
c2 <- 1.791455
fit_xmap <- XMAP(simplify2array(list(R1,R2)), cbind(zs1,zs2),
                 n=c(15000,20000), K = 5,
                 Omega = OmegaHat,
                 Sig_E = c(c1,c2),
                 tol = 1e-6,
                 maxIter = 200, estimate_residual_variance = F, estimate_prior_variance = T,
                 estimate_background_variance = F)
# Get credible set based on R1
cs1 <- get_CS(fit_xmap, Xcorr = R1, coverage = 0.95, min_abs_corr = 0.1)
# Get credible set based on R2
cs2 <- get_CS(fit_xmap, Xcorr = R2, coverage = 0.95, min_abs_corr = 0.1)
# Get joint credible set
cs <- cs1$cs[intersect(names(cs1$cs), names(cs2$cs))]
pip <- get_pip(fit_xmap$gamma)
plot_CS(pip, cs, Beta_true[,1], main = "XMAP")
```
As we can observe, XMAP effectively reduces the PIP of spurious signals and correctly excludes them from the level-95\% credible sets.
